NeuroElectro: A Window to the World's Neuron Electrophysiology Data

### 2014-03-18 neuroelectro_frontiers/main.tex
Added url for repository
Added sciunit reference

\usepackage{url,lineno}
\usepackage{todonotes}

@@

Our future plans are to work with domain ontologists to further develop the existing API into a formal relational data format (RDF) specification, allowing further querying and extending of NeuroElectro into additional resources.

@@

\subsection{Preliminary use of NeuroElectro in scientific work}
The NeuroElectro project is intended to facilitate scientific investigation by providing easy access to large quantities of data about neurons.  
Because the data is machine-readable, we have already begun to conduct several analyses that would not be possible without this resource.  
First, we have begun an investigation of the relationships between neurons defined by the similarity of their electrophysiological properties.  
This information can be used to make predictions about as yet unmeasured properties.  
Second, we have begun to explore the relationship between patterns of gene expression (using both the Allen Brain Atlas and single cell qPCR approaches) and electrophysiological properties of neurons.  
Third, we have begun automated testing of quantitative neuron models, under the reasonable assumption that these models should be constrained by the available experimental data.  
These projects are described in manuscripts currently in preparation.

>>>>

\usepackage{template/url}
\usepackage{template/lineno}

@@

Our future plans are to work with domain ontologists to further develop the existing API into a formal relational data format (RDF) specification, allowing further querying and extending of NeuroElectro into additional resources. All code used in the project and the website is available at \url{http://bitbucket.org/rgerkin/neuroelectro_org}.

@@

\subsection{Preliminary use of NeuroElectro in scientific work}
The NeuroElectro project is intended to facilitate scientific investigation by providing easy access to large quantities of data about neurons.  
Because the data is machine-readable, we have already begun to conduct several analyses that would not be possible without this resource.  
First, we have begun an investigation of the relationships between neurons defined by the similarity of their electrophysiological properties.  
This information can be used to make predictions about as yet unmeasured properties.  
Second, we have begun to explore the relationship between patterns of gene expression (using both the Allen Brain Atlas and single cell qPCR approaches) and electrophysiological properties of neurons.  
Third, we have begun automated testing of quantitative neuron models in concert with SciUnit \citep{omar_sciunit_2014}, under the reasonable assumption that these models should be constrained by the available experimental data.  
These projects are described in manuscripts currently in preparation.
